Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-21 literature/paper_draft.qmd
hierarchy size writing

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
author: Vincent Su
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
execute:
  cache: true
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
---

@@

[This is pasted from the Project Description]{style="color:red;"}

@@

To mitigate these issues, forecast reconciliation was introduced by @Hyndman2011-jv, and later developed by @Hyndman2016-ic, @Wickramasuriya2019-xq, and ... to achieve coherency in point forecasts and enhance accuracy. Forecast reconciliation projects a collection of independent base forecasts into a set of coherent forecasts that respect the linear constraints defining a hierarchical or grouped time-series system.

@@

@@

## Exploring h-step-ahead forecast error metric in NOVELIST Cross-validation

>>>>

---
title: "Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators"
author: Vincent Su
format: 
  pdf:
    include-in-header:
      text: |
        <!-- \usepackage{amsmath} -->
        <!-- \usepackage{mathspec} -->
        \usepackage{algorithm}
        \usepackage{algpseudocode}
        \usepackage[colorlinks=true, linkcolor=blue, citecolor=blue, urlcolor=blue]{hyperref}
        \usepackage{array}
    mathspec: true
    number-sections: true
execute:
  cache: true
  echo: false
  warning: false
bibliography: D:/Github/Recon_Honours_Thesis/references.bib
# bibliographystyle: apa
csl: D:/Github/Recon_Honours_Thesis/apa.csl
---

@@

<!-- [This is pasted from the Project Description]{style="color:red;"} -->

@@

To overcome these issues, forecast reconciliation was introduced by @Hyndman2011-jv, and later developed by @Hyndman2016-ic, @Wickramasuriya2019-xq, and ... to achieve coherency in point forecasts and enhance accuracy. Forecast reconciliation projects a collection of independent base forecasts into a set of coherent forecasts that respect the linear constraints defining a hierarchical or grouped time-series system.

@@

Using the data generating process described above, we consider three different 2-level hierarchical structures, with the bottom-level series $n_b$ being 2 groups of 2 (4 series), 6 groups of 6 (36 series), and 2 groups of 50 (100 series), respectively. The first structure is exactly the same as the one in @fig-hierarchy, with 2 series at the level 1. The second structure has 36 bottom series and are aggregated in groups of size 6 to form 6 level-1 series, which are finally aggregated to form the top level. The third structure is larger, having 100 bottom series aggregated in groups of size 50 to form 2 level-1 series, then aggregated to get the top level. Because of this structure, the VAR(1) coefficients matrix would have entries between groups being zeros. To save space, we will only illustrate the settings of the second structure (6 groups of 6) in @fig-settings-6x6, and the first and third structure is similar.

```{r load results}
#| include: false
library(ggplot2)
library(patchwork)
library(ReconCov)

setwd(getwd())

# sim1_1 <- readRDS("./lib/S4-2-1_T100_M10000_par.rds")
# sim1_2 <- readRDS("./lib/S4-2-1_T300_M10000.rds")
# 
sim2_1 <- readRDS("./lib/S36-6-1_T100_M100_run1.rds")
sim2_2 <- readRDS("./lib/S36-6-1_T300_M100_run2.rds")

# sim3_1 <- readRDS("./lib/S100-2-1_T50_M200_run1.rds")
# sim3_2 <- readRDS("./lib/S100-2-1_T100_M200_run1.rds")
```

```{r generate plots for A and Sigma}
# p1_A <- plot_heatmap(sim1_1$A, T) + 
#   ggtitle("2x2 VAR(1) Coefficients Matrix")
# 
# p1_Sigma <- plot_heatmap(cov2cor(sim1_1$Sigma), T) + 
#   ggtitle("2x2 Correlation Matrix")
# 
p2_A <- plot_heatmap(sim2_1$A) +
  ggtitle("VAR(1) Coefficients Matrix") + theme_void()

p2_Sigma <- plot_heatmap(cov2cor(sim2_1$Sigma), T) +
  ggtitle("Correlation Matrix") + theme_void()

# p3_A <- plot_heatmap(sim3_1$A) +
#   ggtitle("50x2 VAR(1) Coefficients Matrix")
# 
# p3_Sigma <- plot_heatmap(cov2cor(sim3_1$Sigma), T) +
#   ggtitle("50x2 Correlation Matrix")
```

```{r}
#| out.width: "30%"
#| fig.align: "center"
# (p1_A | p1_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r}
#| out.width: "60%"
#| fig.align: "center"
# (p2_A | p2_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r}
#| out.width: "100%"
#| fig.align: "center"
# (p3_A | p3_Sigma) +
#   plot_layout(guides = "collect") & theme(legend.position = "right")
```

```{r fig-settings-6x6}
#| label: fig-settings-6x6
#| fig-cap: "Heatmaps of the VAR(1) coefficient matrix and correlation matrix for the 6×6 structure."
#| out.width: "85%"
#| fig.align: "center"

p2_A + p2_Sigma + plot_layout(ncol = 2) & theme(legend.position = "bottom")
```

@@

## h-step-ahead forecast error metric in NOVELIST Cross-validation
